---
title: '6780'
output:
  pdf_document: default
  html_document: default
---
\textbf{Pr 1}

Answer: (a) According to the given information, we know
\begin{eqnarray*}
[\beta|\sigma_{\epsilon}^2,\alpha,\{\alpha_i,i=1,\cdots,16\},\sigma_{\alpha}^2,\textbf{Y}]&\propto& [\beta,\sigma_{\epsilon}^2,\alpha,\{\alpha_i,i=1,\cdots,16\},\sigma_{\alpha}^2,\textbf{Y}]\propto
[\textbf{Y}|\{\alpha_i,i=1,\cdots,16\},\beta,\sigma_{\epsilon}^2][\beta]\nonumber\\
&\propto&\exp\bigg\{-\frac{\sum_{i=1}^{16}\sum_{j=1}^{12}(y_{ij}-\alpha_i-\beta x_{ij})^2}{2\sigma_{\epsilon}^2}-\frac{\beta^2}{2\times 10^5}\bigg\}\nonumber\\
&\propto&\exp\bigg\{-\beta^2\bigg(\frac{\sum_{i=1}^{16}\sum_{j=1}^{12}x_{ij}^2}{2\sigma_{\epsilon}^2}+\frac{1}{2\times10^5}\bigg)+\beta\bigg(\frac{ \sum_{i=1}^{16}\sum_{j=1}^{12}x_{ij}(y_{ij}-\alpha_i)}{\sigma_{\epsilon}^2}\bigg)\bigg\}
\end{eqnarray*}
which implies $\beta|\sigma_{\epsilon}^2,\alpha,\{\alpha_i,i=1,\cdots,16\},\sigma_{\alpha}^2,\textbf{Y}$ follows $N\Big(\frac{10^5\sum_{i=1}^{16}\sum_{j=1}^{12}x_{ij}(y_{ij}-\alpha_i)}{10^5\sum_{i=1}^{16}\sum_{j=1}^{12}x_{ij}^2+\sigma_{\epsilon}^2},
\frac{10^5\sigma_{\epsilon}^2}{10^5\sum_{i=1}^{16}\sum_{j=1}^{12}x_{ij}^2+\sigma_{\epsilon}^2}\Big)$.


\begin{eqnarray*}
[\sigma_{\epsilon}^2|\beta,\alpha,\{\alpha_i,i=1,\cdots,16\},\sigma_{\alpha}^2,\textbf{Y}]&\propto& [\beta,\sigma_{\epsilon}^2,\alpha,\{\alpha_i,i=1,\cdots,16\},\sigma_{\alpha}^2,\textbf{Y}]\propto
[\textbf{Y}|\{\alpha_i,i=1,\cdots,16\},\beta,\sigma_{\epsilon}^2][\sigma_{\epsilon}^2]\nonumber\\
&\propto&\frac{1}{(\sigma_{\epsilon}^2)^{97.25}}\exp\bigg\{-\frac{\sum_{i=1}^{16}\sum_{j=1}^{12}(y_{ij}-\alpha_i-\beta x_{ij})^2}{2\sigma_{\epsilon}^2}-\frac{0.0005}{\sigma_{\epsilon}^2}\bigg\}
\end{eqnarray*}
which implies $\sigma_{\epsilon}^2|\beta,\alpha,\{\alpha_i,i=1,\cdots,16\},\sigma_{\alpha}^2,\textbf{Y}$ follows $IG(96.25,\frac{1}{2}\sum_{i=1}^{16}\sum_{j=1}^{12}(y_{ij}-\alpha_i-\beta x_{ij})^2+0.0005)$.


\begin{eqnarray*}
&&[\alpha|\beta,\sigma_{\epsilon}^2,\{\alpha_i,i=1,\cdots,16\},\sigma_{\alpha}^2,\textbf{Y}]\propto [\beta,\sigma_{\epsilon}^2,\alpha,\{\alpha_i,i=1,\cdots,16\},\sigma_{\alpha}^2,\textbf{Y}]\propto
[\{\alpha_i,i=1,\cdots,16\}|\alpha,\sigma_{\alpha}^2][\alpha]\nonumber\\
&\propto&\exp\bigg\{-\frac{\sum_{i=1}^{16}(\alpha_i-\alpha)^2}{2\sigma_{\alpha}^2}-\frac{\alpha^2}{2\times10^6}\bigg\}
\propto\exp\bigg\{-\alpha^2\bigg(\frac{8}{\sigma_{\alpha}^2}+\frac{1}{2\times10^6}\bigg)+\frac{\alpha\sum_{i=1}^{16}\alpha_i}{\sigma_{\alpha}^2}\bigg\}
\end{eqnarray*}
which implies $\alpha|\beta,\sigma_{\epsilon}^2,\{\alpha_i,i=1,\cdots,16\},\sigma_{\alpha}^2,\textbf{Y}$ follows $N\Big(\frac{10^6\sum_{i=1}^{16}\alpha_i}{16\times10^{6}+\sigma_{\alpha}^2},\frac{10^6\sigma_{\alpha}^2}{16\times10^{6}+\sigma_{\alpha}^2}\Big)$.

\begin{eqnarray*}
[\{\alpha_i,i=1,\cdots,16\}|\beta,\sigma_{\epsilon}^2,\alpha,\sigma_{\alpha}^2,\textbf{Y}]&\propto& [\beta,\sigma_{\epsilon}^2,\alpha,\{\alpha_i,i=1,\cdots,16\},\sigma_{\alpha}^2,\textbf{Y}]\nonumber\\
&\propto&[\textbf{Y}|\{\alpha_i,i=1,\cdots,16\},\beta,\sigma_{\epsilon}^2]
[\{\alpha_i,i=1,\cdots,16\}|\alpha,\sigma_{\alpha}^2]\nonumber\\
&\propto&\exp\bigg\{-\frac{\sum_{i=1}^{16}\sum_{j=1}^{12}(y_{ij}-\alpha_i-\beta x_{ij})^2}{2\sigma_{\epsilon}^2}
-\frac{\sum_{i=1}^{16}(\alpha_i-\alpha)^2}{2\sigma_{\alpha}^2}\bigg\}\nonumber\\
&\propto&\exp\bigg\{-\sum_{i=1}^{16}\bigg(\frac{6}{\sigma_{\epsilon}^2}+\frac{1}{2\sigma_{\alpha}^2}\bigg)\alpha_i^2
+\alpha_i\bigg(\frac{\sum_{j=1}^{12}(y_{ij}-\beta x_{ij})}{\sigma_{\epsilon}^2}+\frac{\alpha}{\sigma_{\alpha}^2}\bigg)\bigg\}\nonumber\\
\end{eqnarray*}
which implies $\{\alpha_i,i=1,\cdots,16\}|\beta,\sigma_{\epsilon}^2,\alpha,\sigma_{\alpha}^2,\textbf{Y}$ follows $N(\hat{\mu},\hat{\sigma}^2\textbf{I})$,
where $\hat{\mu}=(\hat{\mu}_1,\cdots,\hat{\mu}_{16})$, $\hat{\mu}_i=\frac{\alpha\sigma_{\epsilon}^2+\sum_{j=1}^{12}\sigma_{\alpha}^2(y_{ij}-\beta x_{ij})}{12\sigma_{\alpha}^2+\sigma_{\epsilon}^2}$, $\hat{\sigma}^2=\frac{\sigma_{\alpha}^2\sigma_{\epsilon}^2}{12\sigma_{\alpha}^2+\sigma_{\epsilon}^2}$ and $\textbf{I}$ is the identity matrix.

\begin{eqnarray*}
[\sigma_{\alpha}^2|\beta,\sigma_{\epsilon}^2,\alpha,\{\alpha_i,i=1,\cdots,16\},\textbf{Y}]&\propto& [\beta,\sigma_{\epsilon}^2,\alpha,\{\alpha_i,i=1,\cdots,16\},\sigma_{\alpha}^2,\textbf{Y}]\propto
[\{\alpha_i,i=1,\cdots,16\}|\alpha,\sigma_{\alpha}^2][\sigma_{\alpha}^2]\nonumber\\
&\propto&\frac{1}{(\sigma_{\alpha}^2)^{9.5}}\exp\bigg\{-\frac{\sum_{i=1}^{16}(\alpha_i-\alpha)^2}{2\sigma_{\alpha}^2}-\frac{0.001}{\sigma_{\alpha}^2}\bigg\}
\end{eqnarray*}
which implies $\sigma_{\alpha}^2|\beta,\sigma_{\epsilon}^2,\alpha,\{\alpha_i,i=1,\cdots,16\},\textbf{Y}$ follows $IG(8.5,\frac{1}{2}\sum_{i=1}^{16}(\alpha_i-\alpha)^2+0.001)$.

(b) The R-code is below


```{r}
drug <- read.csv("Baysian Statistics.csv")
sum2<-sum((drug$time)^2)
iteration<-1
beta<-1
sigma_epsilon<-1
alpha<-2
sigma_alpha<-2
a<-rnorm(16,alpha,sqrt(sigma_alpha))
b<-a[1]
for(i in 1:16)
{ if(i==1)
  {
  for(j in 1:11)
    b<-c(b,a[i])
  }
  else
  {
  for(j in 1:12)
    b<-c(b,a[i])
  }
}
```


```{r}
library(invgamma)
while (iteration <= 3500)
{ 
  beta <- c(beta, rnorm(1, mean=1e5*sum(drug$time*(drug$conc-b))/ (1e5*sum2+sigma_epsilon[iteration]), sd = sqrt(1e5*sigma_epsilon[iteration]/(1e5*sum2+sigma_epsilon[iteration]))))
  sigma_epsilon<-c(sigma_epsilon,rinvgamma(1,shape=96.25,rate=0.0005+sum((drug$conc-b-beta[iteration+1]*drug$time)^2)/2))
  alpha<-c(alpha,rnorm(1,mean=(1e6*sum(a))/(16*1e6+sigma_alpha[iteration]),sd=sqrt((1e6*sigma_alpha[iteration])/(16*1e6+sigma_alpha[iteration]))))
  for(i in 1:16)
  {
   d<-drug$conc[drug$subject==i]-beta[iteration+1]*drug$time[drug$subject==i]
   a[i]<-rnorm(1,mean=(alpha[iteration+1]*sigma_epsilon[iteration+1]+sigma_alpha[iteration]*sum(d))/
                 (12*sigma_alpha[iteration]+sigma_epsilon[iteration+1]),
               sd=sqrt((sigma_alpha[iteration]*sigma_epsilon[iteration+1])/
                 (12*sigma_alpha[iteration]+sigma_epsilon[iteration+1])))
  }
  sigma_alpha<-c(sigma_alpha,rinvgamma(1,shape=8.5,rate=0.001+sum((a-alpha[iteration+1])^2)/2))
  
  iteration <- iteration+1 
  b<-a[1]
 for(i in 1:16)
  { if(i==1)
   {
  for(j in 1:11)
    b<-c(b,a[i])
  }
  else
  {
  for(j in 1:12)
    b<-c(b,a[i])
  }
  }
} 
```


```{r}
plot(c(1:3501),beta,type='l',ylim=c(-0.6,-0.4))
plot(c(1:3501),sigma_epsilon,type='l',ylim=c(0,0.5))
plot(c(1:3501),alpha,type='l',ylim=c(0,4))
plot(c(1:3501),sigma_alpha,type='l',ylim=c(0,6))
```

```{r}
plot(density(beta),xlim=c(-0.6,-0.4))
plot(density(sigma_epsilon),xlim=c(0,0.3))
plot(density(alpha))
plot(density(sigma_alpha),xlim=c(0,10))
```


```{r}
acf(beta)
acf(sigma_epsilon)
acf(alpha)
acf(sigma_alpha)
```
```{r}
summary(beta)
summary(sigma_epsilon)
summary(alpha)
summary(sigma_alpha)
```

(c) The R code is below:


```{r}
library(mcmcse)
mcse(beta)
sqrt(1e5*sigma_epsilon[iteration]/(1e5*sum2+sigma_epsilon[iteration]))
```

(d) The R code is below:

```{r}
arima(beta,c(1,0,0))
```

```{r}
-2*7818.49+20*log(16*12)
```


```{r}
arima(beta,c(1,0,1))
```

```{r}
-2*7824.79+20*log(16*12)
```


(e) The R code is below:

```{r}
library(invgamma)
library(coda)
qinvgamma(0.025,shape=8.5,rate=0.001+sum((a-alpha[iteration])^2)/2)
qinvgamma(0.975,shape=8.5,rate=0.001+sum((a-alpha[iteration])^2)/2)
HPDinterval(mcmc(sigma_alpha),0.95)
```


(f) The R code is below:

```{r}
library(coda)
effectiveSize(beta)
effectiveSize(sigma_epsilon)
effectiveSize(alpha)
effectiveSize(sigma_alpha)
```




(g)
\begin{eqnarray*}
[Y|\beta,\sigma_{\epsilon}^2,\alpha,\sigma_{\alpha}^2]&=&\int\cdots\int [Y|\beta,\sigma_{\epsilon}^2,\alpha,\{\alpha_i,i=1,\cdots,16\},\sigma_{\alpha}^2][\{\alpha_i,i=1,\cdots,16\}|\beta,\sigma_{\epsilon}^2,\alpha,\sigma_{\alpha}^2]\prod_{i=1}^{16}d\alpha_i\nonumber\\
&=&\bigg(\frac{1}{2\pi\sigma_{\epsilon}^2}\bigg)^{96}\bigg(\frac{2\sigma_{\epsilon}^2}{12\sigma_{\alpha}^2+\sigma_{\epsilon}^2}\bigg)^8
\exp\bigg\{-\frac{\sum_{i=1}^{16}\sum_{j=1}^{12}(y_{ij}-\beta x_{ij})^2}{2\sigma_{\epsilon}^2}-\frac{8\alpha^2}{\sigma_{\alpha}^2}+\frac{\sum_{i=1}^{16}(\sum_{j=1}^{12}(y_{ij}-\beta x_{ij})\sigma_{\alpha}^2+\alpha\sigma_{\epsilon}^2)^2}{(12\sigma_{\alpha}^2+\sigma_{\epsilon}^2)(2\sigma_{\alpha}^2\sigma_{\epsilon}^2)}\bigg\}
\end{eqnarray*}



















